---
title: How to write functions in R
author: S. Goswami
date: '2021-08-10'
slug: []
categories:
  - R-tutorial
  - workshop
tags:
  - R Markdown
weight: 2
---
```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

## What is a function?

A function is a tool that takes a some input and returns an output.
I am sure most of us  were not taught how to write functions in our basic R class.
Every call that you make daily in your r console is a function
Once you learn how  to write functions, you will get a better understanding of R as a programming language.

## A simple function

Lets start with a simple example, we will call our new function "troy"
```{r}

troy <- function(a,b){
  a+b
}

troy(a = 2, b =4)
## now if we change the values of a and b
troy( a = 5, b =6)
```
So now we have a simple function called troy. 
We can create more complicated functions out of the same.
In fact if you regularly use a set of common r functions, it is a good idea to write a simple function that aggregates your workflow

## Functions to aggregate workflow

```{r,message = FALSE}
#library(mtcars)
library(tidyverse)
data= mtcars
#glimpse(data)

```
Now lets say we follow some data wrangling steps on all data sets and finally generate a plot. 
We can easily create a function that simplifies the process. 
In the following chunk, we take the data mtcar and put all the functions that we want to perform within  a function mtcarplot. 
The idea for this function is that we are avoiding repetition of efforts to generate simple outputs.
This not only reduces the clutter of your code, it also makes you more efficient.


```{r}

mtcarplot <- function(gearnumber){
  data |> filter(gear == gearnumber) |> 
  ggplot(aes(y= mpg, x = disp, color = vs)) +
    geom_point() + 
    geom_smooth(method= "lm")+
    labs(title="Plot of Mileage ~ Displacement")
}
```


Now our function mtcarplot has been created. 
Now all we have to do is change the number associated with "gearnumber" and we will have a fresh plot each time.

> a function in R can have several inputs and based on what  you put inside the {} curly brackets. 
> you get to decide what happens to those inputs and what is returned to you.


```{r, message=FALSE}
mtcarplot(gearnumber = 4)
```


Lets try to change the gear number to 3


```{r, message=FALSE}
mtcarplot(gearnumber = 3) 
```


##   Create your own function

Take a look at your own set of R scripts and see if you can spot some common set of functions that can be joined together to create your own custome function.



